\documentclass[11pt, oneside]{article}   	% use "amsart" instead of "article" for AMSLaTeX format
\usepackage{geometry}                		% See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   		% ... or a4paper or a5paper or ... 
%\geometry{landscape}                		% Activate for for rotated page geometry
%\usepackage[parfill]{parskip}    		% Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}				% Use pdf, png, jpg, or eps with pdflatex; use eps in DVI mode
								% TeX will automatically convert eps --> pdf in pdflatex		
\usepackage{xspace}
\usepackage{amssymb}
\usepackage{cite}
\usepackage{setspace}

\usepackage{xcolor}
\usepackage{xspace}
\def\osprey{{\sc{osprey}}\xspace}
\def\bwmstar{BWM$^*$}
\def\as{\textit{$A^*$}\xspace}
\def\ks{\textit{$K^*$}\xspace}
\def\ka{\textit{$K_a$}\xspace}
\def\bbks{\textit{BBK$^*$}\xspace}


\usepackage{listings}
\lstset{
	basicstyle=\footnotesize
}
\def\submissionMode{0}
\newcommand{\jj}[1]{\if\submissionMode0{\em\color{blue}(JJ: #1)}\else\fi}
\newcommand{\jeff}[1]{\if\submissionMode0{\em\color{blue}(Jeff: #1)}\else\fi}
\newcommand{\suggestion}[1]{\if\submissionMode0{\color{green}\textbf{#1}}\else\fi}
\newcommand{\anna}[1]{\if\submissionMode0{\em\color{purple}(Anna: #1)}\else\fi}


%Submission guidelines for PLoS ONE: http://journals.plos.org/plosone/s/submission-guidelines

\title{{\sc osprey} 3: Open-Source Protein Redesign for You, Refactored, with Powerful New Features}
\author{Mark A. Hallen$^{*,1,3}$, Jeffrey W. Martin$^{*,1}$, Adegoke Ojewole$^{\dagger,4}$, \\
Jonathan D. Jou$^{\dagger,1}$, Anna U. Lowegard$^4$, Marcel S. Frenkel$^5$, Pablo Gainza$^1$, \\
Hunter M. Nisonoff$^1$, Aditya Mukund$^1$, Siyu Wang$^4$, Graham T. Holt$^4$, David Zhou$^1$, \\
Elizabeth Dowd$^1$, and Bruce R. Donald$^{1,2,5}$}
%\date{}							% Activate to display a given date or no date

\begin{document}

%Draft preamble
\if\submissionMode0
{
\textbf{This is a draft of the OSPREY 3.0 release paper. 
\jj{Comments from a particular author are indicated like this.}
Please read and give comments! In particular, please provide suggestions and comments regarding the following issues:
\begin{enumerate}
\item BWM*: JJ has implemented BWM* in a branch of OSPREY 3.0 at this point, but hasn't made it available through the python interface. Should this be a priority?
\item MPLP: Jeff wants to know where we should mention the MPLP bounding implementation, which Hunter and Pablo worked on. This would be the first mention of the work in OSPREY, I believe.
\item Figures: which figures should we add or make?
\end{enumerate}
}
\newpage
}\else\fi

\maketitle
\hspace{-0.25in}$^*,^\dagger$ These authors contributed equally \\
Departments of $^1$ Computer Science and $^2$ Chemistry, Duke University, Durham, NC 27708 \\
$^3$ Toyota Technological Institute at Chicago, Chicago, IL 60637 \\
$^4$ Program in Computational Biology and Bioinformatics and $^5$ Department of Biochemistry, Duke University Medical Center, Durham, NC 27710

%\section{}
%\subsection{}

\if\submissionMode1\singlespacing\else\doublespacing\fi

\section{Abstract}
\input{abstract.tex}

\section{Introduction}
\input{introduction.tex}

\section{Performance enhancements in version 3}
\input{Astar.tex}
\input{GPU.tex}

\jeff{Do we want to mention MPLP here?}
%etc

\section{Python scripting improves ease-of-use}
\input{python.tex}

\section{New protein design algorithms in version 3}
\input{LUTE.tex}
\input{CATS.tex}
\input{BBKS.tex}

\section{Accuracy benchmarks} %\anna{Just adding a section for my part - we can move it wherever we think is best as far as organization goes later.}
\input{KSTests.tex}

\section{Conclusions}
\input{conclusions.tex}

\bibliographystyle{plain}
\bibliography{references}


\end{document}  